Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-19 analysis/paper/paper.Rmd
moved tables back to Table section

@@

```{r abund-data-lp}
LP_mod %>%
  select(event_name, species, data) %>%
  distinct() %>%
  unnest(data) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  rename(`Sampling Event` = event_name,
         Species = species) %>%
  kbl(booktabs = T,
      format.args = list(big.mark = ","),
      caption = "Data summary for single census estimators. M is the number of fish caught in the first sample, marked and returned to the population. n is the number of fish caught in the second sample, and m is the number of marked fish caught in the second sample.") %>%
  kable_styling()
```

```{r abund-data-schn}
N_mods %>%
  select(event_name, species, data) %>%
  distinct() %>%
  unnest(data) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  rename(`Sampling Event` = event_name,
         Species = species,
         Date = date) %>%
  kbl(booktabs = T,
      format.args = list(big.mark = ","),
      caption = "Data summary for multiple census estimators. n is number of fish caught, m is the number of marked fish caught, u is the number of unmarked fish caught, and R is the number of marked fish returned to the population.") %>%
  kable_styling()
```

@@

```{r abund-tab}
all_est %>%
  select(-c(species, range:prop_range)) %>%
  rename(`Sampling Event` = event_name,
         Estimator = model) %>%
  kbl(booktabs = T,
      format.args = list(big.mark = ",")) %>%
  kable_styling()
```

@@

>>>>

# when knitting to Word, use this
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')

if(doc.type == 'docx') {
  options(knitr.table.format = "pandoc")
}

@@

@@

@@

```{r abund-data-lp}
LP_mod %>%
  select(event_name, species, data) %>%
  distinct() %>%
  unnest(data) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  rename(`Sampling Event` = event_name,
         Species = species) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Data summary for single census estimators. M is the number of fish caught in the first sample, marked and returned to the population. n is the number of fish caught in the second sample, and m is the number of marked fish caught in the second sample.") %>%
  kable_styling()

```{r abund-data-schn}
N_mods %>%
  select(event_name, species, data) %>%
  distinct() %>%
  unnest(data) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  rename(`Sampling Event` = event_name,
         Species = species,
         Date = date) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Data summary for multiple census estimators. n is number of fish caught, m is the number of marked fish caught, u is the number of unmarked fish caught, and R is the number of marked fish returned to the population.") %>%
  kable_styling()

```{r abund-tab}
all_est %>%
  select(-c(species, range:prop_range)) %>%
  rename(`Sampling Event` = event_name,
         Estimator = model) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Temporary caption.") %>%
  kable_styling()
